### 2014-02-23 paper/retrofit.tex
wip, no step

iTE  ::=  THole | iTE, lconf id il tS ie

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', (iniTE (lconf id il' tS (iniE ie')))
|}

@@

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iS, (iniTE (lconf id il tS (IT te)))
.-.>
iS, (iniTE (lconf id il tS' (IT te')))
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

@@

>>>>

it   ::=  lconf id il tS ie
iTE  ::=  THole | iTE, it

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', sched step (iniTE (lconf id il' tS (iniE ie')))
|}

@@

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iS, (iniTE (lconf id il tS (IT te)))
.-.>
iS, sched step (iniTE (lconf id il tS' (IT te')))
|}

\and
\inferrule[I-noStep]
{|
it nostep
|}
{|
iS, (iniTE it)
.-.>
iS, sched noStep (iniTE it)
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', sched fork (iniTE' (lconf id' il tS' (TI ie)))
|}
%{|fresh (id')|}

@@

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = it2, ..., it1
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork                    = sched step
\end{code}
  Browbound:
\begin{code}
  sched step                    = Id
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork                    = Id
\end{code}
  Sequential:
\begin{code}
  sched step                       = Id
  sched noStep (it1, it2, ...)     = Id
  sched fork (it1, it2, ... it1n)  = itn, t1, t2, ...
\end{code}
\caption{scheduling policies}
\end{figure}
